Wikipedia Text Mining and Entropy Analysis

### 2019-01-07 childes/childes_entropy.Rmd
working on cogsci

>>>>

get_counts <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1) # uses stems of words, not original words
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
  }

  sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    filter(word_order <= length)
}

get_mean_lengths <- function(role, sen_length, utterances) {

  counts <- get_counts(role, sen_length, utterances)

  lens <- counts %>% 
    group_by(word_order, word) %>% 
    mutate(word_len = str_length(word))

  lens$word_len %>% 
    aggregate(list(lens$word_order), mean)
}

get_entropies <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1) # uses stems of words, not original words
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
  }

  tokens <- sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(word_order, word) %>%
    filter(word_order <= length)

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

### 2019-01-07 cogsci/position-info.Rmd
working on cogsci

@@

# Our Methods

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations. We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains conversations between three young children (over 1.5 years old and under 6 years old) and their families in the home. The Providence corpus contains transcriptions of audio/video files which recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker (child and non-child) and each sentence length within those divisions and computed the unigram entropy measure for each position within those sentence lengths. Plots for the entropy distributions are below. The adult and child unigram entropy distributions track one another extremely well, with the child distribution for each sentence length having relatively lower entropy.

@@

Unlike a UID account

We found a similar distribution for Spanish and German corpora from CHILDES. The Spanish corpus we used was the XXX and the German corpus we used was the XXX.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also use 
markdown formatting to include footnotes using this syntax [^1].

[^1]: Sample of a markdown footnote.

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

>>>>

How do people convey information in speech and text? Is there a regular distribution to how information is conveyed across speech and text? Does speech, with its phonological properties, different from writing, with its semiotic properties, in how information is conveyed?

@@

# Methods

We used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations. We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains conversations between three young children (over 1.5 years old and under 6 years old) and their families in the home. The Providence corpus contains transcriptions of audio/video files which recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

The unigram entropy measure does not directly take into account the context of the utterance.

Figure for the method.

Plots for the entropy distributions are below. The adult and child unigram entropy distributions track one another extremely well, with the child distribution for each sentence length having relatively lower entropy.

@@

We also ran this analysis on Spanish, German, Mandarin and Japanese corpora from CHILDES. The Spanish corpus we used was the XXX and the German corpus we used was the XXX. The Mandarin corpus we used was the XXX and the Japanese corpus we used was the XXX. For Mandarin, we used pinyin transliterations of the utterances in the corpus with demarcated word boundaries, and for Japanese we used romanji transliterations of words in the corpus. Japanese Hiragana, Katakana and Kanji writing systems, and the Chinese characters used for writing Mandarin do not normally demarcate word boundaries. JUSTIFICATION FOR WHY THE TRANSLITERATIONS ARE OKAY.

# Results
We found a distinct three-step distribution for English, Spanish and German CHILDES corpora, with a slight dip in the penultimate position of each sentence. The Mandarin and Japanese data, by comparison,

# Analysis

# Wikipedia Data
We also wanted to apply this analysis to large-scale text data, to compare with the parent-child speech data results from using CHILDES. Using Giuseppe Attardi's Wikiextractor tool \footnote{https://github.com/attardi/wikiextractor}, we extracted the text corpora for $165$ languages from Wikipedia. Each language corpus was cleaned and limited to sentences between $6$ and $50$ words. Similar to the data from CHILDES, we divided each corpus by sentence length, and then computed the unigram entropy measure on each word position within each sentence length. HOW DID WE JOIN TOGETHER SENTENCE LENGTHS

### 2019-01-07 wiki_entropy/wiki_clustering.Rmd
working on cogsci

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(klaR)

library(missMDA)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(klaR)
library(missMDA)
library(clusteval)
library(factoextra)
library(cluster)
